Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-09-24 mice_synthesizing/paper.Rmd
updates

An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993. Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic data sets that can be freely disclosed. Observed data values are then replaced by multiple draws from the posterior predictive distribution of the observed data, based on some imputation model. Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions. Alternatively, the researcher could opt to only replace a subset of the observed data. For example, one can choose to only replace dimensions in the data that could be compared with publicly available data sets or registers. Likewise, synthetisation could be limited to those values that are disclosive, such as high incomes or high turnovers. <!-- I don't think so, because the synthetic values can only be linked to observed values from other sources if they are exactly equal, or if they are the only value within a certain range. The latter might be possible when the number of values is very small, or when the observed value is so extreme that synthetic versions will still be so extreme. However, if the other values are synthetic as well, it is quite likely that synthetic information does not apply to the real-world observation. I think that the highest risk is in the possibility to extract a range of possible values, which might be uniquely match some other record that is available. -->

@@

In `mice`, the generation of multiply imputed data sets is straightforward. The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.

@@

For example, overimputing the observed and missing values in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution

@@

# psych::describe
# correlation matrix
# wgt ~ age + bmi | hgt ~ age + wgt | gen ~ age +

>>>>

An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993. Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic data sets that can be freely disclosed. While in practice, one could see this as replacing the observed data values by multiple draws from the posterior predictive distribution of the observed data, based on some imputation model, Rubin would argue that these synthetic data values are merely draws from the same true data generating model. In that sense, the observed data is never replaced, but the population is resampled from the information captured in the (incomplete) sample. Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions. Alternatively, the researcher could opt to only replace a subset of the observed data. For example, one can choose to only replace dimensions in the data that could be compared with publicly available data sets or registers. Likewise, synthetisation could be limited to those values that are disclosive, such as high incomes or high turnovers. <!-- I don't think so, because the synthetic values can only be linked to observed values from other sources if they are exactly equal, or if they are the only value within a certain range. The latter might be possible when the number of values is very small, or when the observed value is so extreme that synthetic versions will still be so extreme. However, if the other values are synthetic as well, it is quite likely that synthetic information does not apply to the real-world observation. I think that the highest risk is in the possibility to extract a range of possible values, which might be uniquely match some other record that is available. -->

@@

In `mice`, the generation of multiply imputed data sets to solve for unobserved values is straightforward. The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.

@@

For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution

@@

# Simulation setup
- boys data met bootstrap om sampling variance er in te brengen
- wat evalueren we: bias | standard error | coverage
- welke pooling: T = Ubar + B/m

# psych::describe - univariate ok
map --> psych::describe() --> Reduce("+", .) in de pipe

# correlation matrix - relations preserved
map --> cor --> logit --> pool --> inv.logit --> correct diagonal

# wgt ~ age + bmi | hgt ~ age + wgt | gen ~ age + bmi - multivariate ok
3 sets modellen

complete(imp, "all") 
--> lm1
--> lm2
--> polr

pooling cf. T = Ubar + B/m

# Conclusie
- We hebben laten zien dat het belangrijk is om meerdere synthetische versies te creeren. Dit is ook geen probleem, dat doen we immers al decennia lang met imputeren. 
- Waarom geen synthpop --> Ibrahim 2000
- werkt wel goed.
- Beperkingen
- Wat verder nog te doen: aanvullende functies voor complexere combinaties van synthetiseren en imputeren
